Stage-Splitting a Modal Language

### 2014-09-25 paper/semantics.tex
iteration on example/intro

[Check out the example, now staged all fancy.]

This staged version contains three new constructs: 
$\next$ and $\prev$ at the term level, and $\fut$ at the type level.
We can read $\next$ and $\prev$ as indications to 
execute the code in the following block at stage \bbtwo\ and \bbone, respectively.
The type constructor $\fut$ is a way for us to talk at stage \bbone\ about things that will not be available until stage \bbtwo.
Thus, ${\tt fexp} : \fut\rmint \times \rmint \to \fut\rmint$ 
can be read as a function that takes a base at stage \bbtwo\ and a power at stage \bbone, 
and returns the exponent at stage \bbtwo.

[$\fut$ acts in a sanitary way]

>>>>

See [figure part (b)] for a staged version of quickselect.
This example contains all four of the special constructs of \lang: 
$\fut$ at the type level, and $\next$, $\prev$, and $\pause$ at the term level.
Notice that but for these new constructs, the staged version of quickselect is virtually identical to the unstaged version.

The type constructor $\fut$ is a way for us to talk at stage \bbone\ about things that will not be available until stage \bbtwo.
In our example, the type signature ${\tt qs} : {\tt list} \times \fut \rmint \to \fut\rmint$ 
indicates that ${\tt qs}$ is a function that takes a list ($l$) at stage \bbone\ and an integer ($k$) at stage \bbtwo, 
and returns an int at stage \bbtwo\ (the $k$th largest element of $l$).
Note that ${\tt qs}$ is itself bound at stage \bbone.

At the term level, $\pause$ is conceptually the simplest.
It allows us to take an integer computed at stage one, and keep it around until stage \bbtwo.

The staging of a term is achieved via a nesting of alternating $\next$ and $\prev$ blocks.  
As $\next$, $\prev$, and $\pause$ are the only ways in \lang\ to alter the stage of a term,
we surround their arguments with braces in \lang\ syntax.
Specifically, $\next$ embeds a stage \bbtwo\ block within a stage \bbone\ environment,
whereas $\prev$ operates vice versa.
To ensure that information never flows backward in time, 
the output of a $\next$ block is always a $\fut$,
and the only construct that can eliminate $\fut$s is $\prev$.
This means that any values created at stage \bbtwo\ are always handled in a sanitary way while being passed around in stage \bbone.

[still get to WHY we staged like this, and talk about binding time analysis]
